### 2013-11-20 descriptive_analysis.Rmd
All the files and figures moved to GH

% Descriptive visualizations

- [back to index](index.html)

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions")
library(kaRski)
knit("descriptive_analysis.Rmd")
system("pandoc -s descriptive_analysis.md -o descriptive_analysis.html --toc --number-section")

>>>>

# Descriptive visualizations

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions")
library(knitr)
knit2html('descriptive_analysis.Rmd', options = c('toc', markdown::markdownHTMLOptions(TRUE)))

### 2013-11-20 mapPlots.Rmd
All the files and figures moved to GH

% Spatial visualization

- [back to index](index.html)

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit("mapPlots.Rmd")
system("pandoc -s mapPlots.md -o mapPlots.html --toc --number-section")
```

>>>>

# Spatial visualization

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit2html('mapPlots.Rmd', options = c('toc', markdown::markdownHTMLOptions(TRUE)))

```
